Foraging: The Triumphant Return

### 2022-06-09 manuscript.tex

\begin{figure}[H]
\centering
\includegraphics[width=12 cm]{Figures/init_sel_mdl.pdf}
\caption{Posterior fits for (\textit{left}) horizontal and (\textit{right}) vertical locations of the initial target selection. Each line represents a different participant.}
\label{fig:qjep_init_sel_mdl}
\end{figure}

@@

The posterior predictions from the two models are compared in Figure \ref{fig:qjep_init_sel_pred}.

>>>>

\begin{figure}[H]
\centering
\includegraphics[width=12 cm]{Figures/init_sel_mdl.pdf}
\caption{Posterior fits for (\textit{left}) horizontal and (\textit{middle}) vertical locations of the initial target selection. Each line represents a different participant. (\textit{right) A scatter plot showing the $x$ and $y$ posterior means for each participant.}
\label{fig:qjep_init_sel_mdl}
\end{figure}

@@

To compare the two approaches, we assess how well they fit the empirical data: we can use the fitted distributions to calculate the weight assigned to the selected target by each method for each trial in our dataset (Figure \ref{fig:qjep_init_sel_pred}). We can see that both models give a similar distribution of target weights and accuracies. Overall, both methods  select the correct target in around half of the trials. Interesting, as above, there is considerable variation between participants, with participants who favour the top-left corner being easier to predict.
